Initial environmental impacts of Piney Point wastewater discharge into Tampa Bay, Florida

### 2021-08-04 manu-draft.Rmd
very short outline, building refs

---
title: "Title placeholder"
output: 
  bookdown::word_document2:
    reference_docx: my_styles.docx
    number_sections: false
always_allow_html: true
# bibliography: refs.bib
author: "Marcus W. Beck (mbeck@tbep.org), Gary E. Raulerson (graulerson@tbep.org), Maya C. Burke (mburke@tbep.org), Joe Whalen (jwhalen@tbep.org), Sheila Scolaro (sscolar@tbep.org), Ed T. Sherwood (esherwood@tbep.org)"
urlcolor: blue
csl: marine-pollution-bulletin.csl
link-citations: true
---

@@

https://docs.google.com/document/d/1KqaEAYEG7pdcGpWbUjONfVKMHHB6_kOkKCyncp4JYKA/edit

@@

@@

# Conclusions

>>>>

---
title: "Initial environmental impacts of Piney Point wastewater discharge into Tampa Bay, Florida"
output: 
  bookdown::word_document2:
    reference_docx: my_styles.docx
    number_sections: false
always_allow_html: true
bibliography: refs.bib
author: "Marcus W. Beck (mbeck@tbep.org), Gary E. Raulerson (graulerson@tbep.org), Maya C. Burke (mburke@tbep.org), Joe Whalen (jwhalen@tbep.org), Sheila Scolaro (sscolar@tbep.org), Ed T. Sherwood (esherwood@tbep.org)"
urlcolor: blue
csl: marine-pollution-bulletin.csl
link-citations: true
---

@@

* Nutrient management paradigm for southwest Florida estuaries, historical progress
* Threats/challenges to protecting water quality: nutrient inputs, climate change
* Wastewater byproducts from mining are a global threat to the quality of surface and groundwater sources worldwide [@Hudson11].  Phosphate mining industry in Florida, then/now
* Piney Point
* Goals/objectives

@@

* Historical timeline: https://docs.google.com/document/d/1KqaEAYEG7pdcGpWbUjONfVKMHHB6_kOkKCyncp4JYKA/edit
* Initial response, data collection
* Synthesis and Analysis

@@

* 2021 timeline
* Historical context/baseline condition
* effluent characteristics
* water-column water quality changes
* red tide impacts
* Seagrass/macroalgae

# Discussion

* Comparison to other locations/past events - Grand Bay, Bishop Harbor, Huelva estuary [@Perez10;@Perez16]
* Analysis limitations: no smoking gun but 2021 is an anomaly, additional info (benthic diversity TBD, nekton diversity TBD, large mammals, etc.)
* Potential long-term impacts TBD
* Current challenges in TB/southwest FL - OTB, seagrass loss, red tide, climate change
* Risk of decline (IRL ex.)/regression of past progress
